Stability of variational quantum dynamics with Gaussian approximants

### 2013-08-30 paper.tex
writing

The state $|α〉$ is a coherent state with complex amplitude $α$.  These can be defined in a number of ways, perhaps most simply in second quantisation, as eigenstates of a boson annihilation operator $a$, with $a|α〉=α|α〉$.  The annihilation operator is not hermitian, so the eigenvalues $α$ are complex numbers.  In first quantisation, such an operator is the complex amplitude
$$a=(2\hbar)^{-½}(λx+ip/λ),$$
where $x$ and $p$ are the position and momentum operators for a particle with mass $m$.  (The dimensions don't work: $λ²$ is an action, but then $a$ has dimensions.)  The bosons in this case are vibrational quanta in a notional harmonic potential, centred at the origin, with frequency $ω=λ²/m$.

>>>>

The state $|α〉$ is a coherent state with complex amplitude $α$.  These can be defined in a number of ways, perhaps most simply in second quantisation, as eigenstates of a boson annihilation operator $a$, with $a|α〉=α|α〉$.  The annihilation operator is not hermitian, so the eigenvalues $α$ are complex numbers.  In first quantisation, such an operator is the complex amplitude
$$a=(2\hbar)^{-½}(λx+ip/λ),$$
where $x$ and $p$ are the position and momentum operators for a particle with mass $m$.  The bosons in this case are vibrational quanta in a notional harmonic potential, centred at the origin, with frequency $ω=λ²/m$.
